### 2022-05-30 paper.Rmd
typo
words

A simulation study and examples on real norming data showed that the k-plus criterion is well suited to maximize between-group similarity with regard to multiple criteria. In particular, this work indicates that k-plus anticlustering should be a replacement of the classical k-means approach when striving for between-group similarity.[^binarydata]  K-means anticlustering disregards any distribution characteristics other than the mean, while k-plus anticlustering ensures between-group similarity with regard to multiple criteria---and still minimizes differences in means quite well. The results showed that fulfilling several criteria at the same time may be aggregated in small data sets. Still, users can try out different objectives and see which specification fulfils their needs. A reasonable approach it to start greedy by requesting that multiple distribution moments should equalized. Only if the results of the greedy setup are subpar, users can reduce their requirements and opt for fewer criteria. Unlike in statistical analysis, there is no problem with "just trying out" different angles when it comes to anticlustering.

@@

This paper focused on the presentation of new objective function but the did not really consider the multicriterion nature of the k-plus objective. Instead, a simple (unweighted) sum approach---combined with a generic local maximum neighbourhood search---was used to optimize the k-plus objective. Other approaches, such as direct algorithms, may yield improved results and better opportunities to select among partitionings according to multiple differently weighted k-plus criteria. @brusco2019 showed how direct algorithms can be used to optimize multiple critera in anticlustering applications. Their study focused on finding the pareto set of solutions that simultaneously optimize diversity and dispersion -- convincingly arguing that maximizing within-group heterogeneity should incorporate both of these criteria.[^inanticlust] Future research should also investigate how k-plus anticlustering may profit from more sophisticated algorithmic treatment.

>>>>

A simulation study and examples on real norming data showed that the k-plus criterion is well suited to maximize between-group similarity with regard to multiple criteria. In particular, this work indicates that k-plus anticlustering should be a replacement of the classical k-means approach when striving for between-group similarity.[^binarydata]  K-means anticlustering disregards any distribution characteristics other than the mean, while k-plus anticlustering ensures between-group similarity with regard to multiple criteria---and still minimizes differences in means quite well. The results showed that fulfilling several criteria at the same time may be aggregated in small data sets. Still, users can try out different objectives and see which specification fulfils their needs. A reasonable approach is to start greedy by requesting that multiple distribution moments should equalized. If the results of the greedy setup are subpar, users can reduce their requirements by opting for fewer criteria. Unlike in statistical analysis, there is no problem with "just trying out" different angles when it comes to anticlustering.

@@

This paper focused on the presentation of new objective function but the did not really consider the multicriterion nature of the k-plus objective. Instead, a simple (unweighted) sum approach---combined with a generic local maximum neighbourhood search---was used to optimize the k-plus objective. Other approaches, such as direct algorithms, may yield improved results and better opportunities to select among partitionings according to multiple differently weighted k-plus criteria. @brusco2019 showed am example of how direct algorithms can be used to optimize multiple critera in anticlustering applications. Their study focused on finding the pareto set of solutions that simultaneously optimize diversity and dispersion -- convincingly arguing that applications requiring high within-group heterogeneity should incorporate both of these criteria.[^inanticlust] Future research should also investigate how k-plus anticlustering may profit from more sophisticated algorithmic treatment.
